[Re] Non-additive coupling enables propagation of synchronous spiking activity in purely random networks

### 2018-03-07 article/Caze_2018.tex
Update figures in article

\begin{figure}
\centering
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/grid_l_dt_100us_mean.pdf}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_mean.pdf}
\end{subfigure}
\caption{\label{fig:grid}
\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for linearly (A) and non-linearly (B) coupled networks.} For each combination, we initiated synchronous activity with 100 neurons and assessed the stability of the temporal evolution. Blue colouring indicates stable propagation of synchrony, red indicates unstable background activity before onset of propagation, yellow indicates unstable background activity after onset of propagation, and green colouring indicates the absence of propagation (see Methods for details).\\
Replication of Fig.~3a and b in \cite{Memmesheimer2012} (\url{https://doi.org/10.1371/journal.pcbi.1002384.g003})}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{subfigure}[t]{0.33\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/grid_l_dt_100us_gs100_mean.pdf}
\end{subfigure}%
\begin{subfigure}[t]{0.33\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_gs100_mean.pdf}
\end{subfigure}
\begin{subfigure}[t]{0.33\textwidth}
\caption{}\vspace{-1ex}
\includegraphics[width=\textwidth]{Figs/grid_nl_dt_100us_gs75_mean.pdf}
\end{subfigure}
\caption{\label{fig:grid}
\textbf{Qualitative network behaviour as a function of excitatory and inhibitory connection strength for linearly (A) and non-linearly (B, C) coupled networks.} For each combination, we initiated synchronous activity with 100 (A, B) or 75 (C) neurons and assessed the stability of the temporal evolution. Blue colouring indicates stable propagation of synchrony, red indicates unstable background activity before onset of propagation, yellow indicates unstable background activity after onset of propagation, and green colouring indicates the absence of propagation (see Methods for details).\\
Replication of Fig.~3a and b in \cite{Memmesheimer2012} (\url{https://doi.org/10.1371/journal.pcbi.1002384.g003})}
\end{figure}
